### 2023-01-30 manuscript.Rmd
Fix bug in formula

  # Fit an additional control analysis model for the alpha/beta power
  form_alpha_beta <- phase * condition + rt +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models$alpha_beta <- fit_mixed_models(
    dep = "alpha_beta", formula = form_alpha_beta, data = trials
  )

>>>>

  # Fit an additional control analysis model for the alpha/beta power
  form_alpha_beta <- ~ phase * condition + rt +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models$alpha_beta <- fit_mixed_models(
    dep = "alpha_beta", formula = form_alpha_beta, data = trials
  )
